\vspace{-0.5em}\thetitle

### 2009-08-14 paper.tex
...

\title{\vspace{-0.25em}\thetitle}
\author{
{Stefan~Karpinski, John~R.~Gilbert, Elizabeth~M.~Belding} \vspace{0.5em}\\
Department of Computer Science \\
University of California, Santa Barbara \vspace{0.35em}\\
\textit{\{sgk,gilbert,ebelding\}@cs.ucsb.edu}
}

>>>>

\title{\vspace{-0.5em}\thetitle}
\author{
{Stefan~Karpinski, John~R.~Gilbert, Elizabeth~M.~Belding} \vspace{0.75em}\\
Department of Computer Science \\
University of California, Santa Barbara \vspace{0.75em}\\
{\{sgk,gilbert,ebelding\}@cs.ucsb.edu}
}
